Exploration

### 2018-03-05 exploration.Rmd
vectorized sdd F.mx contributions

  #---- Truth: add immigrants
  n.sdd <- nrow(which(sdd[,,2,]==sdd.i, arr.ind=TRUE))
  sdd.j <- which(sdd[,,2,]==sdd.i, arr.ind=TRUE)[,3]
  p.ij <- sdd[,,1,sdd.j][sdd[,,2,sdd.j]==sdd.i]
  for(j in 1:n.sdd) {
    Fs[z.i,z.i,i] <- Fs[z.i, z.i,i] + 
      h*outer(y, y, calc_rcrImm, p=p, p.ij[j], n_seedz=n_seedz, n_flz=n_flz,
              X.seed=X_seed[sdd.j[j],], X.fl=X_fl[sdd.j[j],])
    Fs[1,z.i,i] <- Fs[1,z.i,i] + 
      calc_ImmSB(y, p=p, p.ij[j], n_seedz=n_seedz, n_flz=n_flz,
                            X.seed=X_seed[sdd.j[j],], X.fl=X_fl[sdd.j[j],])
  }

>>>>

  #---- Truth: add immigrants
  sdd.j <- which(sdd[,,2,]==sdd.i, arr.ind=TRUE)[,3]
  p.ij <- sdd[,,1,sdd.j][sdd[,,2,sdd.j]==sdd.i]
  Fs[z.i,z.i,i] <- Fs[z.i,z.i,i] + 
    Reduce(`+`, map2(sdd.j, p.ij, 
                     ~h*outer(y, y, calc_rcrImm, p=p, .y, n_seedz=n_seedz,
                              n_flz=n_flz, X.seed=X_seed[.x,], X.fl=X_fl[.x,])))
  Fs[1,z.i,i] <- Fs[1,z.i,i] + 
    Reduce(`+`, map2(sdd.j, p.ij,
                     ~calc_ImmSB(y, p=p, .y, n_seedz=n_seedz, n_flz=n_flz,
                                 X.seed=X_seed[.x,], X.fl=X_fl[.x,])))
